Reproducing Analyses for Phenotypic evolution is less constrained in complex

### 2018-10-17 analyses/reproduce_analyses.Rmd
created new figure with selection gradients and tidied up some code.

@@

@@

@@

```{r Observe P matrix}

@@

```{r Evo dynamics derived from observed phenotypic variance-covariance, include=FALSE}

@@

```{r altered parameters}
complex_betas
```

@@

```{r Evo-Sim-Hyp-G, echo=FALSE, fig.cap="Evolutionary simulation of a hypothetical G-matrix"}

@@

```{r Compare changes in hypothetical G-matric over time, echo=FALSE}
last(complex_z_feasible$Time)/last(simple_z_feasible$Time)

@@

```{r Generate random G matrices and simulate Evo Dynamics, include=FALSE}

@@

```{r Plot evo sims of many G-matrices, include=FALSE}
evosim.manyG_AF_plot_Diam.Clutch <- AF_plot_Diam.Clutch +
  geom_line(data=sub_tidied_evo_sims, aes(x=Diam, y=Clutch, group=simulation), alpha=0.1)

@@

```{r Evo-Sim-Many-G, echo=FALSE, fig.cap="Evolutionary simulation of a range of G-matrices"}
# Get legend
evosim.manyG_AF_landscape_legend <- get_legend(evosim.manyG_AF_plot_Diam.Pref)

@@

Here we are going to see how fast it took for the *Iteomyia* to hit the edge of the adaptive landscape across many different G-matrices.
```{r Rate of phenotypic evolution, include=FALSE}
evo_sim_duration <-combine_tidied_evo_sims %>%
  group_by(simulation, Foodweb) %>%
  summarise_at(vars(Time), funs(last))

@@

```{r Intuition about evolvability, eval=FALSE}
base_matrix <- matrix(c(1,0,0,
                        0,1,0,
                        0,0,1), nrow=3, ncol=3)
base_G <- 0.5

@@

```{r Intuition about matrix multiplication, eval=FALSE}

@@

```{r Compare evolvabilities at end of simulation, echo=FALSE}

>>>>

Note that there was no effect of food-web structure on on chamber diameter (coef=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$statistic,2)`, 95%CI=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$conf.low,2)`,`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$conf.high,2)`) or female preference (coef=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.log1p.Pref")$statistic,2)`, 95%CI=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.log1p.Pref")$conf.low,2)`,`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.log1p.Pref")$conf.high,2)`).

@@

```{r Average larval survival, cache=TRUE}
model_4_survival_ests <- update(model_4_adj, .~. -1)

boot_model_4_survival_ests <- bootMer(model_4_survival_ests, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)

tidy_model_4_survival_ests <- tidy(boot_model_4_survival_ests, conf.int=T)

tidy_model_4_survival_ests
```

Mean larval survival in complex food web = `r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebComplex")$statistic),2)` [`r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebComplex")$conf.low),2)`,`r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebComplex")$conf.high),2)`].

Mean larval survival in simple food web = `r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebSimple")$statistic),2)` [`r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebSimple")$conf.low),2)`, `r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebSimple")$conf.high),2)`].

@@

## Figure for manuscript

Only use selection gradients for larval parasitoids, use both complex and simple food webs, and only bias adjusted for chamber diameter.

```{r Prep selection gradients figure, echo=FALSE}

focus_gradients <- bind_rows(filter(bias.adj_selection_gradients, term_ord == "Diam" & adjusted == "Yes" | term_ord != "Diam"),
                             filter(egg.larval_selection_gradients, `Food web` == "Larval" & term_ord %in% c("Clutch","Pref^2"))) %>%
  mutate(Type = ifelse(grepl("\\^2", .$term_ord)==TRUE, "Quadratic", ifelse(grepl(":", .$term_ord)==TRUE, "Correlational", "Directional")))

focus_gradients$Type_ord <- factor(focus_gradients$Type, 
                                   levels=c("Directional","Quadratic","Correlational"),
                                   ordered = TRUE)

focus_gradients$axis_x_labels <- as.character(focus_gradients$term_ord)

max_gradient <- max(focus_gradients$`97.5%`)
min_gradient <- min(focus_gradients$`2.5%`)
gradient_limits <- c(-0.3, 0.75)

legend_labels <- c("Egg + Larval (Complex)","Larval parasitoids","Egg parasitoid (Simple)")

directional <- filter(focus_gradients, Type=="Directional") %>%
  ggplot(., aes(x=term_ord)) +
  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=0.5)) +
  geom_point(aes(y=gradient, fill=`Food web`), color="black", size=3, position=position_dodge(width=0.5), shape=21) +
  #coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  ylab("Selection Gradient") +
  scale_fill_manual(values=cbPalette[c(6,4,5)], labels=legend_labels) +
  scale_color_manual(values=cbPalette[c(6,4,5)], labels=legend_labels) +
  facet_wrap(~Type_ord, ncol=2, scales="free_x") +
  scale_x_discrete(name="", labels=parse(text=c("beta[Diam]","beta[Clutch]","beta[Pref]"))) +
  scale_y_continuous(limits = gradient_limits) +
  theme(legend.title.align = 0.5)

quadratic <- filter(focus_gradients, Type=="Quadratic") %>%
  ggplot(., aes(x=term_ord)) +
  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=0.5)) +
  geom_point(aes(y=gradient, fill=`Food web`), color="black", size=3, position=position_dodge(width=0.5), shape=21) +
  #coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  ylab("Selection Gradient") +
  scale_fill_manual(values=cbPalette[c(6,4,5)]) +
  scale_color_manual(values=cbPalette[c(6,4,5)]) +
  facet_wrap(~Type_ord, ncol=2, scales="free_x") +
  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Diam]","gamma[Clutch:Clutch]","gamma[Pref:Pref]"))) +
  scale_y_continuous(limits = gradient_limits)

correlational <- filter(focus_gradients, Type=="Correlational") %>%
  ggplot(., aes(x=term_ord)) +
  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=0.5)) +
  geom_point(aes(y=gradient, fill=`Food web`), color="black", size=3, position=position_dodge(width=0.5), shape=21) +
  #coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  ylab("Selection Gradient") +
  scale_fill_manual(values=cbPalette[c(6,5)]) + # changed from 6,4,5 since larval parasitoids didn't differ for any correlational gradients
  scale_color_manual(values=cbPalette[c(6,5)]) + # same as above
  facet_wrap(~Type_ord, ncol=2, scales="free_x") +
  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Clutch]","gamma[Diam:Pref]","gamma[Clutch:Pref]"))) +
  scale_y_continuous(limits = gradient_limits)
```

Standardized selection gradients estimate selection on a trait in terms of the effects on relative fitness in units of (phenotypic) standard deviations of the trait, allowing direct comparisons among traits, fitness components, and study systems (Kingsolver et al. 2001, Am. Nat.).

```{r Selection-Gradients, echo=FALSE, fig.cap="Selection gradients. Points and lines represents means and 95% confidence intervals (n=1,000 bootstrapped samples)."}

# Get legend
gradients_legend <- get_legend(directional)

# Format plots
gradients_plots <- plot_grid(
  directional + theme(legend.position = "none", axis.title = element_blank()),
  quadratic + theme(legend.position = "none", axis.title = element_blank()),
  correlational + theme(legend.position = "none", axis.title = element_blank()), 
  nrow=2, align="hv", labels = "")
gradients_plots_legend <- ggdraw(gradients_plots) + draw_grob(gradients_legend, x = 0.6, y=-0.2) # x = 0.7, y=-0.2
gradients_y_title <- ggdraw() + draw_label("Selection gradient (SDs)", angle = 90)

gradients_figure <- plot_grid(gradients_y_title, gradients_plots_legend, ncol=2, rel_widths = c(0.05,1))
gradients_figure
```

@@

```{r Observe P matrix, include=FALSE}

@@

```{r Evo dynamics derived from observed phenotypic variance-covariance, include=FALSE, eval=FALSE}

@@

```{r altered parameters, include=FALSE, eval=FALSE}
complex_betas
```

@@

```{r Evo-Sim-Hyp-G, include=FALSE, eval=FALSE, echo=FALSE, fig.cap="Evolutionary simulation of a hypothetical G-matrix"}

@@

```{r Compare changes in hypothetical G-matric over time, echo=FALSE, include=FALSE, eval=FALSE}
last(complex_z_feasible$Time)/last(simple_z_feasible$Time)

@@

```{r Generate random G matrices and simulate Evo Dynamics, include=FALSE, eval=FALSE}

@@

```{r Plot evo sims of many G-matrices, include=FALSE, eval=FALSE}
evosim.manyG_AF_plot_Diam.Clutch <- AF_plot_Diam.Clutch +
  geom_line(data=sub_tidied_evo_sims, aes(x=Diam, y=Clutch, group=simulation), alpha=0.1)

@@

```{r Evo-Sim-Many-G, include=FALSE, eval=FALSE, fig.cap="Evolutionary simulation of a range of G-matrices"}
# Get legend
evosim.manyG_AF_landscape_legend <- get_legend(evosim.manyG_AF_plot_Diam.Pref)

@@

Here we are going to see how fast it took for the *Iteomyia* to hit the edge of the adaptive landscape across many different G-matrices.
```{r Rate of phenotypic evolution, include=FALSE, eval=FALSE}
evo_sim_duration <-combine_tidied_evo_sims %>%
  group_by(simulation, Foodweb) %>%
  summarise_at(vars(Time), funs(last))

@@

```{r Intuition about evolvability, include=FALSE, eval=FALSE}
base_matrix <- matrix(c(1,0,0,
                        0,1,0,
                        0,0,1), nrow=3, ncol=3)
base_G <- 0.5

@@

```{r Intuition about matrix multiplication, include=FALSE, eval=FALSE}

@@

```{r Compare evolvabilities at end of simulation, include=FALSE, eval=FALSE}
